  ---
title: "Intro to Machine Learning with R and Caret"
output: word_document
---

```{R}
library(caret)
library(doSNOW)
#train<-read.csv("C:/Users/iceti/Documents/GitHub/Data-Analyst/Machine_Learning_Caret/train.csv")
train<-read.csv("C:/Users/kun hu/Documents/GitHub/Data-Analyst/Machine_Learning_Caret/train.csv")
#View(train)

```
Replace missing embardked values with mode
```{R}
table(train$Embarked)
train$Embarked[train$Embarked==""]<-"S"
```
Add a feature for tracking missing ages
```{r}
summary(train$Age)
train$missingAge<-ifelse(is.na(train$Age),"Y","N")
```
Add a feature for family size
```{r}
train$FamilySize<-1+train$SibSp+train$Parch
```

Set up factor

```{r}
train$Survived<-as.factor(train$Survived)
train$Pclass<-as.factor(train$Pclass)
train$Sex<-as.factor(train$Sex)
train$Embarked<-as.factor(train$Embarked)
```
Subset data to feature we wish to keep/use
```{r}
features<-c("Survived","Pclass","Sex","Age","SibSp",
            "Parch","Fare","Embarked","missingAge",
            "FamilySize")
train<-train[,features]
str(train)
```

 First, tranform all feature to dummy variables
```{r}
dummy.vars<-dummyVars(~.,data=train[,-1])
train.dummy<-predict(dummy.vars,train[,-1])
```
Impute age
```{r}
pre.process<-preProcess(train.dummy,method="bagImpute")
imputed.data<-predict(pre.process,train.dummy)
#impute age to original data
train$Age<-imputed.data[,6]

```

Use caret to create a 70/30%split of the training data,
keeping rhe proportions of the Survived class label the same across the splits

```{r}
set.seed(54321)
indexes<-createDataPartition(train$Survived,time=1,p=0.7,list=FALSE)
titanic.train<-train[indexes,]
titanic.test<-train[-indexes,]

```

Examine the proportions of survived class lable across the datasets
```{r}
prop.table(table(train$Survived))
prop.table(table(titanic.train$Survived))
prop.table(table(titanic.test$Survived))


```