---
title: "NYPD"
output: html_document
---

First load data into R
```{r}
df<-read.csv("C:/USERS/KUN HU/DESKTOP/NYPD.csv",stringsAsFactors=F,header=T)
str(df)
```
```{r}
summary(df)
```

Load package  
```{r}
library(dplyr)
library(plotly)
library(highcharter)
library(lubridate)
library(ggthemes)
library(tidyr)
library(viridis)
```

```{r}
df$DATE<-mdy(df$DATE)
df$month<-month(df$DATE)
df$year<-year(df$DATE)
df$yearmonth<-substr(df$DATE,0,7)
df$day<-wday(df$DATE)
df$hour<- gsub(":.*$","",df$TIME)
```

Number of Accidents for each borough
```{r}
names(df)
```
Number of accidents for each area
```{r}
df %>% filter(BOROUGH!="") %>%group_by(BOROUGH) %>% summarise(n=sum(n())) %>%  ggplot(aes(x=BOROUGH,y=n,fill=BOROUGH))+geom_bar(position="dodge",stat = "identity")+ggtitle("Number of accidents for each area")+geom_text(aes(label=n),position=position_dodge(1),vjust=-0.2,size=4)

```
We see that Brooklyn has highest accidents while staten island has lowest accidents.

```{r}
df %>% group_by(year) %>% summarise(n=sum(n())) %>%  ggplot(aes(x=year,y=n,fill=n))+geom_bar(position="dodge",stat = "identity")+scale_x_discrete(limits=c("2012","2013","2014","2015","2016","2017"))+xlab("Year")+ylab("Number of accidents")+geom_text(aes(label=n),
position=position_dodge(1),vjust=-0.2,size=4)
```

Number of collisions per month

```{r}
df %>% group_by(month) %>% summarise(n=sum(n())) %>%  ggplot(aes(x=month,y=n,fill=n))+geom_bar(position="dodge",stat = "identity")+scale_x_discrete(limits=c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec"))+xlab("Month")+ylab("Number of accidents")+geom_text(aes(label=n),
position=position_dodge(1),vjust=-0.2,size=2)
```





```{r}
df %>% filter(BOROUGH!="") %>% group_by(day) %>% summarise(n=sum(n())) %>% 
  ggplot(aes(x=day, y=n,fill=n)) +
geom_bar(position="dodge",stat = "identity")+geom_text(aes(label=n),
position=position_dodge(1),vjust=-0.2,size=4)+ggtitle("Day of week accidents counts")+scale_x_discrete(limits=c("Mon","Tue","Wed","Thu","Fri","Sat","Sun"))+ylab("Number of accidents")+xlab("Day")
```

```{R}

df %>% filter(CONTRIBUTING.FACTOR.VEHICLE.1!="Unspecified") %>% group_by(CONTRIBUTING.FACTOR.VEHICLE.1) %>% summarise(n=sum(n())) %>% na.omit() %>%
  
  ggplot(aes(x=reorder(CONTRIBUTING.FACTOR.VEHICLE.1,n), y=n,fill=CONTRIBUTING.FACTOR.VEHICLE.1)) +
geom_bar(position="dodge",stat = "identity")+geom_text(aes(label=n),
position=position_dodge(.9), size=3)+ggtitle("factor accidents counts")+coord_flip()+xlab("Number of accidents")+ylab("Factors to accidents")

```

```{r}
df %>% filter(BOROUGH!="") %>% group_by(hour) %>% summarise(n=sum(n())) %>% na.omit() %>% ggplot(aes(x=hour,y=n,fill=hour))+geom_bar(position="dodge",stat="identity")+scale_x_discrete(limits=c("0","1","2","3","4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20","21","22","23"))+scale_fill_discrete(breaks=c("0","1","2","3","4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20","21","22","23"))+xlab("Hour")+ylab("Number of Accidents")

```
```{r}
df %>% filter(BOROUGH!="") %>% group_by(hour) %>% summarise(n=sum(n())) %>% na.omit() %>% ggplot(aes(x=hour,y=n,fill=hour))+geom_bar(position="dodge",stat="identity")+scale_x_discrete(limits=c("0","1","2","3","4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20","21","22","23"))+scale_fill_discrete(breaks=c("0","1","2","3","4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20","21","22","23"))+xlab("Hour")+ylab("Number of Accidents")

```

Regression model to predict total accidents number during time of the day
independent variable we consider is hour of the day,month, year,day of the week, borough.
```{R}
#subset and pick the independent variables we interested in
#since borough have null value we need to filter them out
df_lm<-subset(df,BOROUGH!="",select=c("day","hour","year","month","BOROUGH"))
#set BOROUGH column as numeric 
df_lm$BOROUGH_dummy<-as.numeric(as.factor(df_lm$BOROUGH))
#set HOUR column as numeric
df_lm$hour<- as.numeric(df_lm$hour)

```

```{r}
hour_of_number<-aggregate(df_lm$hour,by=list(df_lm$year,df_lm$month,df_lm$day,df_lm$BOROUGH_dummy,df_lm$hour),FUN=length)
```

```{r}
colnames(hour_of_number)<-c("Year","Month","Day","Borough","Hour","Accident_Number")
```

Build regression model 
```{r}
lm1<-lm(hour_of_number$Accident_Number~factor(hour_of_number$Year)+factor(hour_of_number$Month)+factor(hour_of_number$Day)+factor(hour_of_number$Borough)+factor(hour_of_number$Hour))

```

```{r}
summary(lm1)
```

Here come to seasonality

```{r}
df %>% group_by(yearmonth) %>% summarise(n=sum(n())) %>%  ggplot(aes(x=yearmonth,y=n,fill=n))+geom_bar(position="dodge",stat = "identity")

```
```{r}
df_hw<-subset(df,yearmonth!="2017-08")
yearmonth_agg<- aggregate(df_hw$yearmonth,by=list(df_hw$yearmonth),FUN=length)
ggplot(data=yearmonth_agg,aes(x=yearmonth_agg$Group.1,y=yearmonth_agg$x,group=1))+geom_line(color="red")+xlab("2012-07 to 2017-08")+ylab("Number of Accidents")+labs(title="Number of accidents from 2012-02 to 2017-07")
```
We can see that number of accidents have seasonality so we maybe can use HoltWinters function to predict future accidents numbers

```{r}
yearmonth_ts<-ts(yearmonth_agg$x,start=c(2012,2),frequency=12)
plot(yearmonth_ts)
hw<-HoltWinters(yearmonth_ts)
forecast<-predict(hw,n.ahead = 12,prediction.interval = T,level = 0.95)
plot(hw,forecast)

```


